True versus apparent shapes of astrophysical bow shocks

### 2017-05-25 papers/Paper1/quadrics-appendix.tex
Make table of equivalence between p-values and number of sigmas
Add the 3-star vs 4+5-star statistics
And lots of minor changes to the tables and figures.

% Landscape table needs to go on its own page, so we need to manually
% adjust the section counter so that it will ``belong'' to the next
% section
\addtocounter{section}{1}
\sisetup{detect-all=true, detect-inline-weight=math}
\sisetup{round-mode=figures, round-precision=2}
\begin{landscape}
\begin{table}
  \setlength\tabcolsep{3pt}
  \caption{Results of all statistical tests performed on observed bow shock shape parameters. Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
  \label{tab:big-p}
  \input{figs/mipsgal-summary-stats-table-body.tex}
\end{table}
\end{landscape}
\begin{table}
  \contcaption{Results of all statistical tests performed on observed
    bow shock shape parameters.}
  \begin{tabular}{p{0.9\linewidth}}
    \toprule
    \textit{Description of columns:}
    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source.
    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.  It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\). 
    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
    (Col.~13)~Ratio of standard deviations between the two sub-samples.
    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}
    (Col.~16)~Brown--Forsythe test for dispersion
    \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
  (b)\\
  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
    tests listed in Table~\ref{tab:big-p}. (a)~Uniformly spaced linear
    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
    bins and logarithmic vertical axis, with all values
    \(p \le 10^{-6}\) included in the leftmost bin.  The vertical dashed
    lines shows the traditional threshold values for significance:
    \(p = 0.001\) and \(p = 0.05\). The red solid line shows the
    uniform distribution of \(p\)-values that would be expected if the
    null hypothesis were always true, that is, if no significant
    correlations existed.}
  \label{fig:histo-p-values}
\end{figure}

>>>>

% Landscape table needs to go on its own page, so we need to manually
% adjust the section counter so that it will ``belong'' to the next
% section
\addtocounter{section}{1}
\sisetup{detect-all=true, detect-inline-weight=math}
\sisetup{round-mode=figures, round-precision=2}
\begin{landscape}
\begin{table}
  \setlength\tabcolsep{3pt}
  \caption{Results of all statistical tests performed on observed bow shock shape parameters. Significant correlations are shown in \textbf{bold}, marginally significant correlations in \textit{italic}}
  \label{tab:big-p}
  \input{figs/mipsgal-summary-stats-table-body.tex}
\end{table}
\end{landscape}
\begin{table}
  \contcaption{Results of all statistical tests performed on observed
    bow shock shape parameters.}
  \begin{tabular}{p{0.9\linewidth}}
    \toprule
    \textit{Description of columns:}
    (Col.~1)~How the two A/B source sub-samples are defined, also giving the size of each sub-sample, \(n_{\text{A}}\) and~\(n_{\text{B}}\).
    (Col.~2)~Dependent variable whose distribution is compared between the two sub-samples.
    (Cols.~3--6)~Mean and standard deviation, \(\sigma\), of the dependent variable for each of the two sub-samples.
    (Cols.~7--8)~Mean over each sub-sample of the observational dispersion (\(\epsilon\), standard deviation) of radii that contribute to the dependent variable for each individual source.
    (Cols.~9--10)~``Standard error of the mean'' (s.e.m.) of the dependent variable for each of the two sub-samples. 
    (Cols.~11--13)~Standardized ``effect sizes'', which are dimensionless measures of the difference in the distribution of the dependent variable between the two sub-samples.
    (Col.~11)~Rank biserial correlation coefficient \citep{Cureton:1956a}, which is obtained by considering all \(n_{\text{A}} n_{\text{B}}\) pair-wise comparisons of the dependent variable between a source in sub-sample~A and a source in sub-sample~B.  It is the difference between the fraction of such comparisons ``won'' by sub-sample~A and those ``won'' by sub-sample~B, and thus may vary between \(-1\) and \(+1\). 
    (Col.~12)~Cohen's \(d\), which is a dimensionless mean difference: \(d = (\langle \text{A} \rangle - \langle \text{B} \rangle) / \sigma_{\text{pool}} \), where \(\sigma_{\text{pool}} = (n_{\text{A}} \sigma_{\text{A}}^2 + n_{\text{B}} \sigma_{\text{B}}^2)^{1/2} / \sqrt{n_{\text{A}} + n_{\text{B}}}\) is the pooled standard deviation.
    (Col.~13)~Ratio of standard deviations between the two sub-samples.
    (Cols.~14--16)~Probabilities (\(p\)-values) of the two sub-samples being as different as observed if they were to be drawn from the same population, according to three different non-parametric tests.
    (Col.~14)~Anderson--Darling 2-sample test, which is a general test of similarity between two distributions that is designed to retain sensitivity to differences in the tails of the distributions.
    (Col.~15)~Mann--Whitney--Wilcoxon \(U\) test \citep{Mann:1947a}, which is sensitive 
    (Col.~16)~Brown--Forsythe test for equality of variance \citep{Brown:1974a}
    \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\begin{figure}
  (a)\\
  \includegraphics[width=\linewidth]{figs/p-value-histogram-new-linear}\\
  (b)\\
  \includegraphics[width=\linewidth]{figs/p-value-histogram-new}
  \caption{Histogram of \(p\)-values for all non-parametric 2-sample
    tests listed in Table~\ref{tab:big-p}. (a)~Uniformly spaced linear
    bins and linear vertical axis. (b)~Uniformly spaced logarithmic
    bins and logarithmic vertical axis, with all values
    \(p \le 10^{-6}\) included in the leftmost bin.  Short thin vertical
    lines above the horizontal axis show the individual value.  The
    thick vertical dashed lines shows the traditional threshold values
    for significance: \(p = 0.003\) (\(\approx 3 \sigma\)) and
    \(p = 0.05\) (\(\approx 2 \sigma\)). The red solid line shows the uniform
    distribution of \(p\)-values that would be expected if the null
    hypothesis were always true, that is, if no significant
    correlations existed.}
  \label{fig:histo-p-values}
\end{figure}

### 2017-05-25 papers/Paper1/sec-quadrics-observations.tex
Add the 3-star vs 4+5-star statistics
And lots of minor changes to the tables and figures.

The KDE contours in Figure~\ref{fig:mipsgal-shapes}b show that the
distribution of 3-star sources is very similar to that of 4- and
5-star sources, although the higher-rated sources are shifted slightly
to the upper right.  This is probably due to higher-rated sources
being on average bigger, as will be discussed further below.  The bulk
of the sources are concentrated around the paraboloid line, with
\(1 < R_c/R_0 < 2.5\), and \(1.2 < R_{90}/R_0 < 2\).  But significant
minorities are found in three other regions: (1)~a clump with
\(R_c/R_0 \la 1\); (2)~a vertical spur towards higher \(R_{90}\) at
\(R_c/R_0 \approx 2\); and (3)~a broad horizontal tail towards higher
\(R_c\) at \(R_{90}/R_0 \la 2\).

@@

The second example (Fig.~\ref{fig:mipsgal-uncorrelated}b) divides the
sources according to whether or not \citet{Kobulnicky:2016a} judged
there to be multiple candidates for identity of the central star that
drives the bow shock.  If the central star were to be misidentified,
then the measured value of \(R_0\) would be erroneous, which would
increase the dispersion in both \(R_c/R_0\) and \(R_{90}/R_0\).  The
fact that no significant difference is seen in the shape distributions
between sources with/without multiple candidates implies that such
mistakes in identification of the central star must be rare.

>>>>

The KDE contours in Figure~\ref{fig:mipsgal-shapes}b show that the
distribution of 3-star sources is very similar to that of 4- and
5-star sources, although the higher-rated sources are shifted slightly
to the upper right.  Possible reasons for this are discussed in
\S~\ref{sec:corr-shape} below.
% This is probably due to higher-rated sources
% being on average bigger, as will be discussed further below.
The bulk of the sources are concentrated around the paraboloid line,
with \(1 < R_c/R_0 < 2.5\), and \(1.2 < R_{90}/R_0 < 2\).  But
significant minorities are found in three other regions: (1)~a clump
with \(R_c/R_0 \la 1\); (2)~a vertical spur towards higher \(R_{90}\)
at \(R_c/R_0 \approx 2\); and (3)~a broad horizontal tail towards higher
\(R_c\) at \(R_{90}/R_0 \la 2\).

@@

The second example (Fig.~\ref{fig:mipsgal-uncorrelated}b) divides the
sources according to whether or not \citet{Kobulnicky:2016a} judged
there to be multiple candidates for the identity of the central star
that drives the bow shock.  If the central star were to be
misidentified in a significant number of sources, then the measured
value of \(R_0\) for those sources would be erroneous, which would
increase the scatter in both \(R_c/R_0\) and \(R_{90}/R_0\).  The
fact that no significant difference is seen in the shape distributions
between sources with/without multiple candidates implies that such
mistakes in identification of the central star must be rare.

We also tested all the other source parameters listed in
\citeauthor{Kobulnicky:2016a}'s catalog, finding no significant shape
differences for sources with/without \SI{8}{\um} emission, with
low/high extinction, closer/farther from the Galactic plane, or
closer/farther from the Galactic center. Details are given in
Table~\ref{tab:big-p}.  In all these cases, differences in mean or
median \(R_{90}/R_0\) less than \(0.06\) and in \(R_c/R_0\) less than
\(0.16\) are found, which are not significant even at the 2-\(\sigma\)
level.

The only parameters that \emph{do} show a possible correlation with
the bowshock shape are the bow shock angular size, \(R_0\), and the
extinction-corrected magnitude of the central star, \(H_0\), which are
illustrated

As mentioned in \S~\ref{sec:ob-shapes} there is also a shape
difference between the 3-star sources and the 4/5-star sources (see
Fig.~\ref{fig:mipsgal-shapes}b).  The \(p\)-values of statistical
tests (see Table~\ref{tab:big-p}) indicate that this is much more
significant than any correlation with the other parameters discussed
in this section (\(p < 10^{-4}\) for \(R_{90}/R_0\) and
\(p < 10^{-5}\) for \(R_c/R_0\)).  This means that it cannot be simply
due to the tendency of the higher-rated sources to have larger angular
sizes.  However, the subjective nature of the star ratings makes this
hard to interpret.
